Imputation

### 2017-07-22 imputation.Rmd
3rd run of imputation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r, results='hide'}
library(bigsnpr)
library(dplyr)
library(ggplot2)

@@

bigstatsr:::MY_THEME(ggplot(), coeff = 1.8) +
  geom_histogram(aes(maf)) + 
  labs(x = "Minor Allele Frequency")

@@

bigstatsr:::MY_THEME(ggplot(), coeff = 1.8) +
  geom_histogram(aes(nbNA), bins = 100) + 
  labs(x = "Number of missing values")

@@

## Imputation with our new method

```{r}
system.time(
  infos <- snp_fastImpute(GNA, infos.chr = popres$map$chromosome, ncores = NCORES)
) # Latest timings: 42 / 48 minutes
```

```{r}
# Errors
mean(XNA[indNA] != X[indNA]) # 4.7 / 4.8 %
table(XNA[indNA], X[indNA])

@@

## Imputation with BEAGLE

@@

```{r}
system.time(
  bedfile2 <- snp_beagleImpute(beagle.path = BEAGLE,
                               plink.path = PLINK,
                               bedfile.in = "backingfiles/tmp.bed",
                               memory.max = 30,
                               ncores = NCORES)
) # 14.6 / 14.2 hours
```

@@

mean(X_beagle[indNA] != X[indNA]) # 3.1 / 4.8 %
table(X_beagle[indNA], X[indNA])
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center", fig.width = 15)
```

@@

```{r, message=FALSE}
library(bigsnpr)
library(dplyr)
library(ggplot2)

@@

bigstatsr:::MY_THEME(ggplot(), coeff = 2) +
  geom_histogram(aes(maf)) + 
  labs(x = "Minor Allele Frequency")

@@

bigstatsr:::MY_THEME(ggplot(), coeff = 2) +
  geom_histogram(aes(nbNA), bins = 100) + 
  labs(x = "Number of missing values")

@@

## Imputation with the new method based on XGBoost

```{r}
system.time(
  infos <- snp_fastImpute(GNA, infos.chr = popres$map$chromosome, ncores = NCORES)
) # Previous runs: 42 / 48 / 48 minutes
```

```{r}
# Errors
mean(XNA[indNA] != X[indNA]) # 4.7 / 4.8 / 4.8 %
table(XNA[indNA], X[indNA])

@@

## Imputation with BEAGLE (called via bigsnpr)

@@

```{r}
system.time(
  bedfile2 <- snp_beagleImpute(beagle.path = BEAGLE,
                               plink.path = PLINK,
                               bedfile.in = "backingfiles/tmp.bed",
                               memory.max = 30,
                               ncores = NCORES)
) # 14.6 / 14.2 / 14.0 hours
```

@@

mean(X_beagle[indNA] != X[indNA]) # 3.1 / 4.8 / 4.8 %
table(X_beagle[indNA], X[indNA])
```
